---
title: "tidyverse recepies"
author: "Peter Kowalchuk"
date: "December 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Income Statement Wide Table Generator

###Summary
The following R script loads income statements from EDGAR and builds a wide table with entries for all companies. For this exercise Google and Facebook are added to the table.


#### Load Libraries

The finreportr package is used to scrape data out of the EDGAR site together with the tidyverse package

```{r}
#install.packages("finreportr")
#install.packages("tidyverse")
```

finreportr and tidyverse libraries are loaded

```{r}
library(finreportr)
library(tidyverse)
library(kableExtra)
```

### Load income statements

Income statement for Google is loaded

```{r}
inc_g<-GetIncome("GOOG", 2017)
inc_g %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

Amazon income statement is loaded

```{r}
inc_a<-GetIncome("AMZN", 2017)
inc_a %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

### Build wide tables

A wide table for Google is created

```{r}
inc_wide_g<-inc_g %>% spread(Metric,Amount)
inc_wide_g <- inc_wide_g %>% mutate(company="Google")
inc_wide_g %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

A wide table for Amazon is created

```{r}
inc_wide_a<-inc_a %>% spread(Metric,Amount)
inc_wide_a <- inc_wide_a %>% mutate(company="Amazon")
inc_wide_a %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

A wide table containing all companies is created

```{r}
inc_all<-bind_rows(inc_wide_a,inc_wide_g)
inc_all %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

### Extract only reveneu data

**Find columns with revenue**
```{r}
rev <- inc_all %>% select(endDate,company,starts_with("Revenue")) 
rev %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
rev_col<-colnames(rev)
rev_col<-rev_col[3:length(rev_col)]
```

**Build new long table with revenues**

```{r}
rev_only <- rev %>% unite('Revenue',rev_col)
rev_only <- rev_only[!(rev_only$Revenue=="NA_NA"),]
rev_only$Revenue<-gsub("[^0-9\\.]", "", rev_only$Revenue)
rev_only <- rev_only %>% group_by(company)
rev_only %>% kable() %>% kable_styling() %>% scroll_box(height = "400px")
```

#### Improvements

- Plot data as a bar chart
- Add a third company
- Add a company with a different fiscal cycle

#### References

https://cran.r-project.org/web/packages/finreportr/vignettes/finreportr.html

https://www.sec.gov/edgar.shtml


