---
title: "tidyverse"
author: "Peter Kowalchuk"
date: "December 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Income Statement Wide Table Generator

The following R script loads income statements from EDGAR and builds a wide table with entries for all companies. For this exercise Google and Facebook are added to the table.

The finreportr package is used to scrape data out of the EDGAR site

```{r}
install.packages("finreportr")
```

finreportr and tidyverse libraries are loaded

```{r}
library(finreportr)
library(tidyverse)
```

Income statement for Google is loaded

```{r}
inc_g<-GetIncome("GOOG", 2017)
inc_g
```

A wide table for Google is created

```{r}
inc_wide_g<-inc_g %>% spread(Metric,Amount)
inc_wide_g <- inc_wide_g %>% mutate(company="Google")
inc_wide_g
```

Facebook income statement is loaded

```{r}
inc_f<-GetIncome("FB", 2017)
inc_f
```

A wide table for Facebook is created

```{r}
inc_wide_f<-inc_f %>% spread(Metric,Amount)
inc_wide_f <- inc_wide_f %>% mutate(company="Facebook")
inc_wide_f
```

A wide table containing all companies is created

```{r}
inc_all<-bind_rows(inc_wide_f,inc_wide_g)
inc_all
```

